\documentclass{mumie.element.exercise}
%$Id$
\begin{metainfo}
  \name{
    \lang{de}{Ü07: Monotonie}
    \lang{en}{Exercise 7}
  }
  \begin{description} 
 This work is licensed under the Creative Commons License Attribution 4.0 International (CC-BY 4.0)   
 https://creativecommons.org/licenses/by/4.0/legalcode 

    \lang{de}{Hier die Beschreibung}
    \lang{en}{}
  \end{description}
  \begin{components}
  \end{components}
  \begin{links}
  \end{links}
  \creategeneric
\end{metainfo}
\begin{content}
\title{
  \lang{de}{Ü07: Monotonie}
  \lang{en}{Exercise 7}
}





\begin{block}[annotation]
  TODO: Konzeption 2
\end{block}

\begin{block}[annotation]
  Im Ticket-System: \href{http://team.mumie.net/issues/9106}{Ticket 9106}
\end{block}

\lang{de}{Gegeben sei die Funktion $f(x)=x\ln x$ f\"{u}r $x>0$. Wo steigt $f$ monoton, wo f\"{a}llt $f$ monoton? 
Wo besitzt $f$ station\"{a}re Stellen?}
\lang{en}{Let $f(x)=x\ln x$ for $x>0$. Where is $f$ monotonically increasing and where is $f$ monotonically decreasing? Where are the stationary points of $f$?}


\begin{tabs*}[\initialtab{0}\class{exercise}]
  \tab{
  \lang{de}{Antwort}
  \lang{en}{Answer}
  }
\lang{de}{$f$ ist auf dem Intervall $(0;e^{-1})$ monoton fallend und auf dem Intervall 
$(e^{-1};\infty)$ monoton steigend. In $e^{-1}$ liegt die einzige station\"{a}re Stelle vor.}
\lang{en}{$f$ is monotonically decreasing in the interval $(0,e^{-1})$ and monotonically increasing in the interval $(e^{-1},\infty)$. There is a single stationary point which is at $e^{-1}$.}

  \tab{
  \lang{de}{L\"{o}sung}
  \lang{en}{Solution}
  }
  \begin{incremental}[\initialsteps{1}]
  \step \lang{de}{Wir berechnen $f'(x)$ mit der Produktregel.}
  \lang{en}{We calculate $f'(x)$ with the product rule.}
  \step \[f'(x)=\ln x+x\frac{1}{x}=\ln x+1.\]
   \step 
  
  \lang{de}{Wir setzen $f'(x)=0$ an:}
  \lang{en}{We set $f'(x)=0$:}
  
  \[0=\ln x+1.\]
  \lang{de}{Dies gilt genau dann, wenn $x=e^{-1}$ ist. Also liegt in $e^{-1}$ die einzige station\"{a}re Stelle vor.}
  \lang{en}{This is only true when $x=e^{-1}$. Thus there exists only one stationary point which is at $e^{-1}$.}
   \step \lang{de}{Da $\ln x+1<0$ f\"{u}r $x\in (0; e^{-1})$, ist $f$ dort monoton fallend, und sogar streng monoton fallend.}
   \lang{en}{Since $\ln x+1<0$ for $x\in (0, e^{-1})$, $f$ is monotonically decreasing there. In fact, $f$ is strictly monotonically decreasing.}
   
   \step \lang{de}{Da $\ln x+1>0$ f\"{u}r $x\in (e^{-1};\infty)$, ist $f$ dort monoton steigend, und sogar streng monoton steigend.}
   \lang{en}{Since $\ln x+1>0$ for $x\in (e^{-1},\infty)$, $f$ is monotonically increasing there. In fact, $f$ is strictly monotonically increasing.}


   
  
  \end{incremental}


\end{tabs*}

\end{content}